---
title: "Bayes Final Project"
author: "Hannah Snell"
date: "11/30/2020"
output: html_document
---
# Data Setup 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(bayesrules)
library(rstan)
library(readr)
library(rstanarm)
library(bayesplot)
```

```{r}
covid <- read_csv("time1Time2Data.csv")
time_1 <- read_csv("Sheet 1-Table 1-1.csv")
```


# Variable EDA and Selection  

## 12/3/2020 Game Plan

Outcome: _Overall Quality of Life Score_

### LIST OF VARIABLES IN TIME 1 DATA: 
(Mark if they need any kind of cleaning)



Dianne's list:
Gender
Age (I think theres 1 N/A to clean)
Occupation (needs lost of cleaning)
Employment status
Marital status
Education
Race
Income (clean NAs)
Illnesses and meds yes/no
isolation yes/no
perceived susceptibility
Quality of life total
Patient Health questionnaire total



Natalia:
age 
gender (binary)
illnesses (binary)
education (scale)
percieved vulnerability to disease
percieved vulnerability to COVID
impact of events scale total
intolerance of uncertainty total
preventative action taken scale PPE use
five factor mindfulness questionairre total
general health questionairre total
isolation (binary)

Elaine: 
Age
gender 
Employment status
Education 
Accomodation 
Self-isolation (yes/no)
General health questionnaire 
Prevention action taken scale PPE use 
Quality of life 
Patient health quationnaire 
Intolerance of uncertainty 
Perceived susceptibility to COVID 19 
Perceived susceptibility to disease 










Hannah's List - Predictor Vars
- Age (no cleaning needed)
- Gender (no cleaning needed) 
- Occupation (RELEVEL)
- Employment Status Before/After COVID
- Marital Status
- Education
- Race
- Religion (Reshape)
- State (Relevel)
- Isolation
- Perceived Susceptibility to COVID
- FFMQ Total Vars 

# Predicting Quality of Life 

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
pois_mod2 <- stan_glm(Time1_quality_of_life_Total ~ Time1_Illnesses + Time1_general_health_quetionnaire_total + Time1_five_factor_mindfulness_questionnaire_total + Time1_Illnesses*Time1_general_health_quetionnaire_total + Time1_general_health_quetionnaire_total*Time1_five_factor_mindfulness_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total*Time1_Illnesses, 
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(pois_mod2, nreps = 50)

# Trace plots of parallel chains
mcmc_trace(pois_mod2, size = 0.1)
#look fine

# Density plots of parallel chains
mcmc_dens_overlay(pois_mod2)
#looks fine, chains have stabilized

model_summary <- summary(pois_mod2)
head(as.data.frame(model_summary), -2)


predictions <-posterior_predict(pois_mod2,
  newdata = covid)

ppc_intervals(covid$Time1_quality_of_life_Total,
yrep = predictions,
prob = 0.5, prob_outer = 0.95)
#not sure how to interpret this

set.seed(84735)
#cv_procedure <- prediction_summary_cv(
#data = covid, model = pois_mod2, k = 10)

#cv_procedure$cv
#within 50 not great, but mae_scaled not too bad
```

Can we get the middle/peak more accurate?

#Predicting Self-Isolation (Logistic Regression)

```{r echo=TRUE, results = 'hide'}
covid_bin <- covid %>%
  mutate(Time1_self_isolation_yes_or_no = if_else(Time1_self_isolation_yes_or_no == '1', '0', '1')) %>%
    mutate(Time1_self_isolation_yes_or_no = as.integer(Time1_self_isolation_yes_or_no))

set.seed(84735)
log_mod <- stan_glm(Time1_self_isolation_yes_or_no   ~ Time1_patient_health_questionnaire_total +  Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total*Time1_impact_of_events_scale_total ,
                        data = covid_bin,
                        family = binomial('logit'),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(log_mod)
```


# Predicting Perceived Vulnerability to Disease At Time 2

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
disease_mod3 <- stan_glm(Time2_perceived_vulnerability_to_disease_total ~ Time2_Illnesses + Time2_Meds + Time2_intolerance_of_uncertainty_total + Time2_impact_of_events_scale_total + Time2_Illnesses*Time2_Meds + Time2_intolerance_of_uncertainty_total*Time2_impact_of_events_scale_total,
                        data = covid,
                        family = gaussian(),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(disease_mod3, nreps = 50)
```

This is not perfect, but closest I have gotten so far... can we improve?

# Predicting Preventative Action: Avoiding Travel and People

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
cov_mod6 <- stan_glm(Time1_preventive_action_taken_scale_avoid_travel_people ~
Time1_Age + Time1_Gender + Time1_Marital_status +  Time1_five_factor_mindfulness_questionnaire_total + Time1_Religious_Affiliation + Time1_Age*Time1_Marital_status,
                     data = covid,
                     family = poisson(),
                     chains = 4,
                     iter = 5000*2)
                       
pp_check(cov_mod6, nreps = 50)
```

This is the best model I can get so far... poisson works best 


# Predicting PPE Use

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
ppe_6 <- stan_glm(Time1_preventive_action_taken_scale_PPEuse ~ Time1_Age +
Time1_intolerance_of_uncertainty_total + Time1_five_factor_mindfulness_questionnaire_total +  Time1_intolerance_of_uncertainty_total:Time1_five_factor_mindfulness_questionnaire_total,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(ppe_6, nreps = 50)
```

This is the best model I have gotten, but still having trouble fitting the bimodaality.





# Elaine's model; predicting quality of life
```{r echo=TRUE, results = 'hide'}
#Model b: Elaine's initial model
set.seed(84735)
model_b <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education +  Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)

set.seed(84735)
pp_check(model_b, nreps = 50)
model_summary <- summary(model_b)
head(as.data.frame(model_summary), -2)

#Model b2: add `Illnesses` to Elaine's model
set.seed(84735)
mod_b2 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education +  Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_b2, nreps = 50)
model_summary2 <- summary(mod_b2)
head(as.data.frame(model_summary2), -2)


#pois_mod2: Natalia's from above, but with data from time_1 instead of covid (more data points):
set.seed(84735)
pois_mod2 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Illnesses + General_Health_Questionnaire_Negative_Total + FFMQtotal + Illnesses*General_Health_Questionnaire_Negative_Total + General_Health_Questionnaire_Negative_Total*FFMQtotal + FFMQtotal*Illnesses, 
                             data = time_1,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(pois_mod2, nreps = 50)
model_summary <- summary(pois_mod2)
head(as.data.frame(model_summary), -2)


#adding `Illnesses` and interaction terms to Elaine's Model b
#THIS IS THE BEST SO FAR!
set.seed(84735)
mod_c <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total + Patient_Health_Questionnaire_Total*Illnesses + Illnesses*General_Health_Questionnaire_Negative_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c, nreps = 50)


#Elaine's Model b2 (adding Illnesses) as poisson
set.seed(84735)
mod_d <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses +  General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total,
                             data = time_1,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_d, nreps = 50)
```

```{r}
loo_elaine <- loo(model_b)
loo_elaine2 <- loo(mod_b2)
#by visual comparison of these 2 models: mod_2b is better, so only use loo_elaine2

loo_n1 <- loo(pois_mod2)
loo_n2 <- loo(mod_c)
loo_n3 <- loo(mod_d)

loo_compare(loo_n1, loo_n2, loo_n3, loo_elaine2)

#Model c seems to be best 
pp_check(mod_c, nreps = 50)
```

```{r echo=TRUE, results = 'hide'}
#test whether we need all the interaction terms in model c?

#mod c without any interaction terms
set.seed(84735)
mod_c2 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c2, nreps = 50)


#mod c with only first int term
set.seed(84735)
mod_c3 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c3, nreps = 50)


#mod c with first 2 interaction terms
set.seed(84735)
mod_c4 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total + Patient_Health_Questionnaire_Total*Illnesses,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c4, nreps = 50)


#mod c: add FFMQ score
set.seed(84735)
mod_c5 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + FFMQtotal + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total + Patient_Health_Questionnaire_Total*Illnesses + Illnesses*General_Health_Questionnaire_Negative_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c5, nreps = 50)

#add interaction between health and FFMQ
set.seed(84735)
mod_c6 <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + FFMQtotal + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total + Patient_Health_Questionnaire_Total*Illnesses + Illnesses*General_Health_Questionnaire_Negative_Total + Intolerance_of_Uncertainty_Total*FFMQtotal,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_c6, nreps = 50)


#compare models
loo_int <- loo(mod_c)
loo_no <- loo(mod_c2)
loo_one <- loo(mod_c3)
loo_two <- loo(mod_c4)
loo_more <- loo(mod_c5)
loo_moreint <- loo(mod_c6)
loo_compare(loo_int, loo_no, loo_one, loo_two, loo_more, loo_moreint)

#model c5 is the best!! go with that one for now
```
