---
title: "data_cleaning"
author: "Hannah Snell"
date: "12/5/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)

timeone <- read_csv("Sheet 1-Table 1-1.csv")
```

# Clean Variables

```{r}
# State Variable 
timeone_clean <- timeone %>% 
  mutate(State = tolower(State)) %>% 
  mutate(State = recode(State, 
                           "alabama" = "AL",
                           "alaska" = "AK",
                           "arizona" = "AZ",
                           "arkansas" = "AR",
                           "california" = "CA",
                           "colorado" = "CO",
                           "connecticut" = "CT",
                           "delaware" = "DE",
                           "district Of Columbia" = "DC",
                           "florida" = "FL",
                           "georgia" = "GA",
                           "hawaii" = "HI",
                           "idaho" = "ID",
                           "illinois" = "IL",
                           "indiana" = "IN", 
                           "iowa" = "IA",
                           "kansas" = "KS",
                           "kentucky" = "KY",
                           "louisiana" = "LA", 
                           "maine" = "ME",
                           "maryland" = "MD",
                           "massachusetts" = "MA",
                           "michigan" = "MI",
                           "minnesota" = "MN",
                           "mississippi" = "MS",
                           "missouri" = "MO",
                           "montana" = "MT",
                           "nebraska" = "NE",
                           "nevada" = "NV",
                           "new hampshire" = "NH",
                           "new jersey" = "NJ",
                           "new mexico" = "NM",
                           "new york" = "NY",
                           "north carolina" = "NC",
                           "north dakota" = "ND",
                           "ohio" = "OH",
                           "oklahoma" = "OK",
                           "oregon" = "OR",
                           "pennsylvania" = "PA",
                           "rhode island" = "RI",
                           "south carolina" = "SC",
                           "south dakota" = "SD",
                           "tennessee" = "TN",
                           "texas" = "TX",
                           "utah" = "UT",
                           "vermont" = "VT",
                           "virginia" = "VA",
                           "washington" = "WA",
                           "west virginia" = "WV",
                           "wisconsin" = "WI",
                           "wyoming" = "WY")) %>% 
  mutate(State = tolower(State)) %>% 
  # get list of typos to adjust here
  #filter(nchar(State) > 2) %>% 
  #filter(State != "usa") %>% 
  mutate(State = recode(State,  "penssylvania" =  "PA", 
                                "pennyslavania" = "PA",  
                                "pensynlvannia" = "PA",  
                                "north corilon" = "NC", 
                                "taxas" = "TX", 
                                "newjersey" = "NJ", 
                                "oklahamo" = "OK", 
                                "new y ork" = "NY", 
                                "lousiana" = "LA",  
                                "colampya" = "None", 
                                "america" = "usa", 
                                "oregan" = "OR", 
                                "maxcico" = "None", 
                                "ckoforin" = "NY",  
                                "united states" = "usa")) %>% 
  mutate(State = toupper(State)) %>% 
   mutate(State = str_replace(State, ".*TODAY.*", "NONE"))
  
```

For the occupation variable, I am using the U.S. Bureau of Labor Statistics SOC Codes for Labor Categories: 

11-0000  Management Occupations
13-0000  Business and Financial Operations Occupations
15-0000  Computer and Mathematical Occupations
17-0000  Architecture and Engineering Occupations
19-0000  Life, Physical, and Social Science Occupations
21-0000  Community and Social Service Occupations
23-0000  Legal Occupations
25-0000  Educational Instruction and Library Occupations
27-0000  Arts, Design, Entertainment, Sports, and Media Occupations
29-0000  Healthcare Practitioners and Technical Occupations
31-0000  Healthcare Support Occupations
33-0000  Protective Service Occupations
35-0000  Food Preparation and Serving Related Occupations
37-0000  Building and Grounds Cleaning and Maintenance Occupations
39-0000  Personal Care and Service Occupations
41-0000  Sales and Related Occupations
43-0000  Office and Administrative Support Occupations
45-0000  Farming, Fishing, and Forestry Occupations
47-0000  Construction and Extraction Occupations
49-0000  Installation, Maintenance, and Repair Occupations
51-0000  Production Occupations
53-0000  Transportation and Material Moving Occupations
55-0000  Military Specific Occupations

```{r}
# Overwrite w Occupation Variable 

timeone_clean <- read_csv("timeone_clean_20201209.csv")

# Tidy Data  

timeone_clean <- timeone_clean %>% 
  mutate(Religion = case_when(Religion_Protestant == 1 ~ "Protestant", 
                              Religion_Roman_Catholic == 1 ~ "Roman Catholic", 
                              Religion_Mormon == 1 ~ "Mormon", 
                              Religion_Jewish == 1 ~ "Jewish", 
                              Religion_Agnostic == 1 ~ "Agnostic", 
                              Religion_Atheist == 1 ~ "Atheist", 
                              Religion_Buddhist == 1 ~ "Buddhist", 
                              Religion_Hindu == 1 ~ "Hindu", 
                              Religion_Nothing_in_particular == 1 ~ "Nothing in Particular", 
                              Religion_Something_else == 1 ~ "Something Else")) %>% 
  select(-(Religion_Protestant:Religion_12_describe), -City, -Country, -Meds_2_describe, -Illnesses_2_describe)

write_csv(timeone_clean, "timeone_clean.csv")

```

# References 

[standard occupational classifications - u.s. dept labor stats](https://www.bls.gov/soc/2018/major_groups.html)
