---
title: "data_cleaning"
author: "Hannah Snell"
date: "12/5/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)
library(mice)
library("MissMech") # install from local file https://cran.r-project.org/src/contrib/Archive/MissMech/ 

timeone <- read_csv("Sheet 1-Table 1-1.csv")
```

# Clean Variables

```{r}
# State Variable 
timeone_clean <- timeone %>% 
  mutate(State = tolower(State)) %>% 
  mutate(State = recode(State, 
                           "alabama" = "AL",
                           "alaska" = "AK",
                           "arizona" = "AZ",
                           "arkansas" = "AR",
                           "california" = "CA",
                           "colorado" = "CO",
                           "connecticut" = "CT",
                           "delaware" = "DE",
                           "district Of Columbia" = "DC",
                           "florida" = "FL",
                           "georgia" = "GA",
                           "hawaii" = "HI",
                           "idaho" = "ID",
                           "illinois" = "IL",
                           "indiana" = "IN", 
                           "iowa" = "IA",
                           "kansas" = "KS",
                           "kentucky" = "KY",
                           "louisiana" = "LA", 
                           "maine" = "ME",
                           "maryland" = "MD",
                           "massachusetts" = "MA",
                           "michigan" = "MI",
                           "minnesota" = "MN",
                           "mississippi" = "MS",
                           "missouri" = "MO",
                           "montana" = "MT",
                           "nebraska" = "NE",
                           "nevada" = "NV",
                           "new hampshire" = "NH",
                           "new jersey" = "NJ",
                           "new mexico" = "NM",
                           "new york" = "NY",
                           "north carolina" = "NC",
                           "north dakota" = "ND",
                           "ohio" = "OH",
                           "oklahoma" = "OK",
                           "oregon" = "OR",
                           "pennsylvania" = "PA",
                           "rhode island" = "RI",
                           "south carolina" = "SC",
                           "south dakota" = "SD",
                           "tennessee" = "TN",
                           "texas" = "TX",
                           "utah" = "UT",
                           "vermont" = "VT",
                           "virginia" = "VA",
                           "washington" = "WA",
                           "west virginia" = "WV",
                           "wisconsin" = "WI",
                           "wyoming" = "WY")) %>% 
  mutate(State = tolower(State)) %>% 
  # get list of typos to adjust here
  #filter(nchar(State) > 2) %>% 
  #filter(State != "usa") %>% 
  mutate(State = recode(State,  "penssylvania" =  "PA", 
                                "pennyslavania" = "PA",  
                                "pensynlvannia" = "PA",  
                                "north corilon" = "NC", 
                                "taxas" = "TX", 
                                "newjersey" = "NJ", 
                                "oklahamo" = "OK", 
                                "new y ork" = "NY", 
                                "lousiana" = "LA",  
                                "colampya" = "None", 
                                "america" = "usa", 
                                "oregan" = "OR", 
                                "maxcico" = "None", 
                                "ckoforin" = "NY",  
                                "united states" = "usa")) %>% 
  mutate(State = toupper(State)) %>% 
   mutate(State = str_replace(State, ".*TODAY.*", "NONE"))
  
```

For the occupation variable, I am using the U.S. Bureau of Labor Statistics SOC Codes for Labor Categories: 
11-0000  Management Occupations
13-0000  Business and Financial Operations Occupations
15-0000  Computer and Mathematical Occupations
17-0000  Architecture and Engineering Occupations
19-0000  Life, Physical, and Social Science Occupations
21-0000  Community and Social Service Occupations
23-0000  Legal Occupations
25-0000  Educational Instruction and Library Occupations
27-0000  Arts, Design, Entertainment, Sports, and Media Occupations
29-0000  Healthcare Practitioners and Technical Occupations
31-0000  Healthcare Support Occupations
33-0000  Protective Service Occupations
35-0000  Food Preparation and Serving Related Occupations
37-0000  Building and Grounds Cleaning and Maintenance Occupations
39-0000  Personal Care and Service Occupations
41-0000  Sales and Related Occupations
43-0000  Office and Administrative Support Occupations
45-0000  Farming, Fishing, and Forestry Occupations
47-0000  Construction and Extraction Occupations
49-0000  Installation, Maintenance, and Repair Occupations
51-0000  Production Occupations
53-0000  Transportation and Material Moving Occupations
55-0000  Military Specific Occupations

```{r}
# Overwrite w Occupation Variable 

timeone_clean <- read_csv("timeone_clean_20201209.csv")

# Tidy Data  

timeone_clean <- timeone_clean %>% 
  mutate(Religion = case_when(Religion_Protestant == 1 ~ "Protestant", 
                              Religion_Roman_Catholic == 1 ~ "Roman Catholic", 
                              Religion_Mormon == 1 ~ "Mormon", 
                              Religion_Jewish == 1 ~ "Jewish", 
                              Religion_Agnostic == 1 ~ "Agnostic", 
                              Religion_Atheist == 1 ~ "Atheist", 
                              Religion_Buddhist == 1 ~ "Buddhist", 
                              Religion_Hindu == 1 ~ "Hindu", 
                              Religion_Nothing_in_particular == 1 ~ "Nothing in Particular", 
                              Religion_Something_else == 1 ~ "Something Else")) %>% 
  dplyr::select(-(Religion_Protestant:Religion_12_describe), -City, -Country, -Meds_2_describe, -Illnesses_2_describe)

#write_csv(timeone_clean, "timeone_clean.csv")

```

## From Association Model

```{r}
#time_1 <- read_csv("Sheet 1-Table 1-1.csv")
timeone_clean <- timeone_clean %>%
  # filter(is.na(General_Health_Questionnaire_Negative_Total)==FALSE) %>%
  # filter(is.na(Age)==FALSE) %>%
  # filter(is.na(Gender)==FALSE) %>%
  # filter(is.na(Education)==FALSE) %>%
  # filter(is.na(Intolerance_of_Uncertainty_Total)==FALSE) %>%
  # filter(is.na(FFMQtotal)==FALSE) %>%
  # filter(is.na(Patient_Health_Questionnaire_Total)==FALSE) %>%
  # filter(is.na(Illnesses)==FALSE) %>%
  # filter(is.na(Perceived_Vulnerability_to_Disease_Total)==FALSE) %>%
  # filter(is.na(Perceived_susceptibility_COVID)==FALSE) %>%
  # filter(is.na(Annual_income)==FALSE) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID %in% c(4, 5, 6, 7), "unemployed")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID %in% c(1,2), "parttime")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == 3, "fulltime")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "unemployed", 0)) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "parttime", 1)) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "fulltime", 2)) %>%
  mutate(Employment_status_After_COVID = as.numeric(Employment_status_After_COVID)) %>% 
  mutate(Annual_income = log(Annual_income)) %>%
  mutate(Marital_status = replace(Marital_status, Marital_status %in% c(1, 5, 6), 0)) %>%
  mutate(Marital_status = replace(Marital_status, Marital_status %in% c(2, 3, 4), 1)) %>%
  mutate(Illnesses = replace(Illnesses, Illnesses == 1, 0)) %>%
  mutate(Illnesses = replace(Illnesses, Illnesses == 2, 1)) %>%
  mutate(Gender = replace(Gender, Gender == 1, 0)) %>%
  mutate(Gender = replace(Gender, Gender == 2, 1)) %>%
  mutate(Isolation_yesorno = replace(Isolation_yesorno, Isolation_yesorno == 1, 0)) %>%
  mutate(Isolation_yesorno = replace(Isolation_yesorno, Isolation_yesorno == 2, 1))
```


## From LASSO

```{r}
# 1. Remove variables that we won't use:  
timeone_clean <- timeone_clean %>% 
  dplyr::select(-Occupation, -`ID_case#`, -`Date`)

# 2. Find the total NA's per variable: 
# varsNA <- as.data.frame(sapply(timeone_clean, function(x) sum(is.na(x))))
# 
# # 3. Extra data cleaning before multiple imputation: 
# 
# # Isolate a small df of all the vars with NA's 
# colnames(varsNA)[1] <- "NAs"
# varsNA <- varsNA %>% 
#   filter(NAs != 0)

# Clean all the vars with NA's (the ones that we won't imputate)
timeone_clean <- timeone_clean %>% 
  mutate(`SOC Category` = replace_na(`SOC Category`, "Unknown"), 
         State = replace_na(State, "Unknown"),  
         State = recode(State, "USA" = "Unknown"), 
         State = recode(State, "NONE" = "Unknown"),
         State = recode(State, "US" = "Unknown"), 
         State = recode(State, "GE" = "GA"),
         State = recode(State, "NEW  YORK" = "NY"), 
         State = recode(State, "34" = "Unknown"),
         Isolation_number_of_days = replace_na(Isolation_number_of_days, 0),  
         Religion = replace_na(Religion, "Unknown")) 

colnames(timeone_clean)[3] <- "SOC_Category"

timeone_clean <- timeone_clean %>% 
  mutate(State_dummy =  recode(State, 
                           "AL" = 1,
                           "AK" = 2,
                           "AZ" = 3,
                           "AR" = 4,
                           "CA" = 5,
                           "CO" = 6,
                           "CT" = 7,
                           "DE" = 8,
                           "DC" = 9,
                           "FL" = 10,
                           "GA" = 11,
                           "HI" = 12,
                           "ID" = 13,
                           "IL" = 14,
                           "IN" = 15, 
                           "IA" = 16,
                           "KS" = 17,
                           "KY" = 18,
                           "LA" = 19, 
                           "ME" = 20,
                           "MD" = 21,
                           "MA" = 22,
                           "MI" = 23,
                           "MN" = 24,
                           "MS" = 25,
                           "MO" = 26,
                           "MT" = 27,
                           "NE" = 28,
                           "NV" = 29,
                           "NH" = 30,
                           "NJ" = 31,
                           "NM" = 32,
                           "NY" = 33,
                           "NC" = 34,
                           "ND" = 35,
                           "OH" = 36,
                           "OK" = 37,
                           "OR" = 38,
                           "PA" = 39,
                           "RI" = 40,
                           "SC" = 41,
                           "SD" = 42,
                           "TN" = 43,
                           "TX" = 44,
                           "UT" = 45,
                           "VT" = 46,
                           "VA" = 47,
                           "WA" = 48,
                           "WV" = 49,
                           "WI" = 50,
                           "WY" = 51,
                           "Unknown" = 0),
         Religion_dummy = recode(Religion, 
                           "Protestant" = 1, 
                           "Roman Catholic" = 2,  
                           "Hindu" = 3, 
                           "Buddhist" = 4, 
                           "Mormon" = 5,  
                           "Jewish" = 6, 
                           "Agnostic" = 7, 
                           "Atheist" = 8, 
                           "Nothing in Particular" = 9, 
                           "Something Else" = 10, 
                           "Unknown" = 0
                           ),
         SOC_Category_dummy = recode(SOC_Category, 
                              "Management Occupations" = 1, 
                              "Business and Financial Operations Occupations" = 2, 
                              "Computer and Mathematical Occupations" = 3, 
                              "Architecture and Engineering Occupations" = 4, 
                              "Life, Physical, and Social Science Occupations" = 5, 
                              "Community and Social Service Occupations" = 6, 
                              "Legal Occupations" = 7, 
                              "Educational Instruction and Library Occupations" = 8, 
                              "Arts, Design, Entertainment, Sports, and Media Occupations" = 9,
                              "Healthcare Practitioners and Technical Occupations" = 10, 
                              "Healthcare Support Occupations" = 11, 
                              "Protective Service Occupations" = 12, 
                              "Food Preparation and Serving Related Occupations" = 13,  
                              "Building and Grounds Cleaning and Maintenance Occupations" = 14, 
                              "Personal Care and Service Occupations" = 15, 
                              "Sales and Related Occupations" = 16, 
                              "Office and Administrative Support Occupations" = 17, 
                              "Farming, Fishing, and Forestry Occupations" = 18, 
                              "Construction and Extraction Occupations" = 19, 
                              "Installation, Maintenance, and Repair Occupations" = 20, 
                              "Production Occupations" = 21, 
                              "Transportation and Material Moving Occupations" = 22, 
                              "Military Specific Occupations" = 23,  
                              "Unknown" = 0)
 ) %>% 
   dplyr::select(-SOC_Category, -State, -Religion)
```

(Removed categorical vars and used dummy vars for LASSO model)

```{r}
# Little's MCAR Test to check for complete randomness in missing values before imputation
time_1 <- read_csv("Sheet 1-Table 1-1.csv")
time1_miss <- time_1 %>%
  dplyr::select(Gender, Age, Employment_status_Befor_COVID, Employment_status_After_COVID, Marital_status, Education, Race, Annual_income, Illnesses, Meds, Accomodation, Isolation_yesorno, Isolation_number_times_leave_per_day, Perceived_susceptibility_COVID, FFMQtotal, Patient_Health_Questionnaire_Total, Quality_of_Life_Total, General_Health_Questionnaire_Negative_Total, Perceived_Vulnerability_to_Disease_Total, Intolerance_of_Uncertainty_Total, Preventive_Action_Taken_Scale_PPEuse_Total, Preventive_Action_Taken_Scale_Avoid_Travel_People_Total, Impact_of_Events_Scale_Total, Number_of_children)
test <- TestMCARNormality(time1_miss)
print(test)
summary(time_1)
```

```{r}
# 4. Imputate Age, Annual_income, Illnesses, Meds, Isolation_number_times_leave_per_day, Perceived_susceptibility_COVID: 
imputated_timeone <- mice(timeone_clean, m = 5, meth ='pmm', seed = 84735)
# summary(imputated_timeone)

p1 <- densityplot(imputated_timeone) # i think this is good? probably needs reviewing

complete_timeone <- complete(imputated_timeone, 1)

write_csv(complete_timeone, "timeone_clean.csv")
```


# References 

[standard occupational classifications - u.s. dept labor stats](https://www.bls.gov/soc/2018/major_groups.html)
