---
title: "Bayes Final Project"
author: "Hannah Snell, Natalia Iannucci, Dianne Caravela, Elaine Ya"
date: "12/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(bayesrules)
library(rstan)
library(readr)
library(rstanarm)
library(bayesplot)
```

# Title


# Abstract 


# Background and Significance

### Literature Review

### Select Variables

```{r}
covid <- read_csv("time1Time2Data.csv")
time_1 <- read_csv("Sheet 1-Table 1-1.csv")
time_1 <- time_1 %>%
  filter(is.na(General_Health_Questionnaire_Negative_Total)==FALSE) %>%
  filter(is.na(Age)==FALSE) %>%
  filter(is.na(Gender)==FALSE) %>%
  filter(is.na(Education)==FALSE) %>%
  filter(is.na(Intolerance_of_Uncertainty_Total)==FALSE) %>%
  filter(is.na(FFMQtotal)==FALSE) %>%
  filter(is.na(Patient_Health_Questionnaire_Total)==FALSE) %>%
  filter(is.na(Illnesses)==FALSE) %>%
  filter(is.na(Perceived_Vulnerability_to_Disease_Total)==FALSE) %>%
  filter(is.na(Perceived_susceptibility_COVID)==FALSE) %>%
  filter(is.na(Annual_income)==FALSE) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID %in% c(4, 5, 6, 7), "unemployed")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID %in% c(1,2), "parttime")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == 3, "fulltime")) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "unemployed", 0)) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "parttime", 1)) %>%
  mutate(Employment_status_After_COVID = replace(Employment_status_After_COVID, Employment_status_After_COVID == "fulltime", 2)) %>%
  mutate(Annual_income = log(Annual_income)) %>%
  mutate(Marital_status = replace(Marital_status, Marital_status %in% c(1, 5, 6), 0)) %>%
  mutate(Marital_status = replace(Marital_status, Marital_status %in% c(2, 3, 4), 1)) %>%
  mutate(Illnesses = replace(Illnesses, Illnesses == 1, 0)) %>%
  mutate(Illnesses = replace(Illnesses, Illnesses == 2, 1)) %>%
  mutate(Gender = replace(Gender, Gender == 1, 0)) %>%
  mutate(Gender = replace(Gender, Gender == 2, 1)) %>%
  mutate(Isolation_yesorno = replace(Isolation_yesorno, Isolation_yesorno == 1, 0)) %>%
  mutate(Isolation_yesorno = replace(Isolation_yesorno, Isolation_yesorno == 2, 1))
```


control for demographics (age, sex, educational attainment)

### hypothesis

# Methods

examine distribution to determine type of regression (poisson, gaussian, binom, etc)

Create model
## One for predicting quality of life

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
mod_QOL_orig <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + Intolerance_of_Uncertainty_Total + FFMQtotal + Patient_Health_Questionnaire_Total + Illnesses + General_Health_Questionnaire_Negative_Total + Perceived_Vulnerability_to_Disease_Total + Patient_Health_Questionnaire_Total*General_Health_Questionnaire_Negative_Total + Patient_Health_Questionnaire_Total*Illnesses + Illnesses*General_Health_Questionnaire_Negative_Total,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)
set.seed(84735)
pp_check(mod_QOL_orig, nreps = 50)


# Trace plots of parallel chains
mcmc_trace(mod_QOL_orig, size = 0.1)
#look fine

# Density plots of parallel chains
mcmc_dens_overlay(mod_QOL_orig)
#looks fine, chains have stabilized
```

```{r}
set.seed(84735)
cv <-prediction_summary_cv(
data = time_1, model = mod_QOL_orig, k = 10)

cv$cv

# mae 3.187955
# mae scaled 0.9042877 
# 50% 0.5427273 
# 90% 0.9416667

model_summary <- summary(mod_QOL_orig)
head(as.data.frame(model_summary), -2)
```


```{r}
#THIS IS OUR FINAL MODEL! ((I Think at least...))
set.seed(84735)
mod_QOL_final <- stan_glm(Quality_of_Life_Total ~ Age + as.factor(Gender) + Education + FFMQtotal + Patient_Health_Questionnaire_Total + as.factor(Illnesses) + General_Health_Questionnaire_Negative_Total + as.factor(Employment_status_After_COVID) + as.factor(Marital_status) + Annual_income + Isolation_yesorno,
                             data = time_1,
                             family = gaussian,
                             chains = 4,
                             iter = 5000*2)

set.seed(84735)
pp_check(mod_QOL_final, nreps = 50)

model_summary_final <- summary(mod_QOL_final)
head(as.data.frame(model_summary_final), -2)
```

## One for predicitng PPE use

Run diagnostics 

Evaluate Accuracy 

Interpret model

# Results


# Discussion/Conclusion


# References 