---
title: "Natalia Working Doc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bayesrules)
library(rstan)
library(readr)
library(rstanarm)
library(bayesplot)
```

```{r message=FALSE, warning=FALSE}
covid <- read_csv("time1Time2Data.csv")
```

```{r include=FALSE}
covid %>%
  select(Time1_Age,Time1_Race, Time1_Illnesses, Time1_impact_of_events_scale_total, Time1_Educational_attainment, Time1_meds, Time1_patient_health_questionnaire_total,Time1_perceived_susceptibility_to_COVID19 ,Time1_general_health_quetionnaire_total, Time1_Employment_After_COVID, Time1_intolerance_of_uncertainty_total, Time1_intolerance_of_uncertainty_total, Time1_Gender, Time1_perceived_vulnerability_to_disease,Time1_self_isolation_yes_or_no,Time1_number_of_times_leave_home_per_day, Time1_preventive_action_taken_scale_avoid_travel_people,Time1_Marital_status, Time1_five_factor_mindfulness_questionnaire_total, Time1_Religious_Affiliation, Time1_preventive_action_taken_scale_avoid_travel_people, Time1_preventive_action_taken_scale_PPEuse, Time1_quality_of_life_Total) %>%
  as.data.frame() %>%
  cor(use="complete.obs")
```

```{r include=FALSE}
covid %>%
  select(Time2_Annual_income,Time2_Illnesses,Time2_Meds, Time2_impact_of_events_scale_total, Time2_employment_status, Time2_patient_health_questionnaire_total, Time2_intolerance_of_uncertainty_total ,Time2_perceived_susceptibility_to_covid19 ,Time2_self_isolation_yes_or_no, Time2_five_factor_mindfulness_questionnaire_total, Time2_general_health_questionnaire_total, Time2_perceived_vulnerability_to_disease_total,Time2_preventive_action_taken_scale_PPEuse, Time2_quality_of_life_total) %>%
  as.data.frame() %>%
  cor(use="complete.obs")
```







# PREDICTING QUALITY OF LIFE

Time1_quality_of_life_Total
  predictors: illnesses, health_questionairere, percieved suscept, mindfulness, general health quest, percieved vuln to disease 
  
```{r echo=TRUE, results = 'hide'}
set.seed(84735)
quality_mod1 <- stan_glm(Time1_quality_of_life_Total ~ Time1_patient_health_questionnaire_total + Time1_perceived_vulnerability_to_disease + Time1_five_factor_mindfulness_questionnaire_total + Time1_patient_health_questionnaire_total*Time1_perceived_vulnerability_to_disease, 
                             data = covid,
                             family = gaussian(),
                             chains = 4,
                             iter = 5000*2)

pp_check(quality_mod1, nreps = 50)
```

###Poisson model better; copied into main RMD 

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
pois_mod <- stan_glm(Time1_quality_of_life_Total ~ Time1_Illnesses + Time1_perceived_susceptibility_to_COVID19 + Time1_five_factor_mindfulness_questionnaire_total, 
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(pois_mod, nreps = 50)




set.seed(84735)
pois_mod2 <- stan_glm(Time1_quality_of_life_Total ~ Time1_Illnesses + Time1_general_health_quetionnaire_total + Time1_five_factor_mindfulness_questionnaire_total + Time1_Illnesses*Time1_general_health_quetionnaire_total + Time1_general_health_quetionnaire_total*Time1_five_factor_mindfulness_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total*Time1_Illnesses, 
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(pois_mod2, nreps = 50)
```




Time1_perceived_susceptibility_to_COVID19 
  predictors: Time1_patient_health_questionnaire_total, Time1_impact_of_events_scale_total, Time1_intolerance_of_uncertainty_total, Time1_perceived_vulnerability_to_disease, Time1_five_factor_mindfulness_questionnaire_total   

# PREDICTING PERCIEVED SUSCEPTIBILITY:

## to COVID: can we get this weird multimodality?

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
cov_mod <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_Illnesses + Time1_impact_of_events_scale_total+ Time1_perceived_vulnerability_to_disease + Time1_perceived_vulnerability_to_disease*Time1_general_health_quetionnaire_total, 
                             data = covid,
                             family = poisson,
                             chains = 4,
                             iter = 5000*2)


pp_check(cov_mod, nreps = 50)
```

```{r echo=TRUE, results = 'hide'}
#Miles said to try Poisson
set.seed(84735)
susceptibility_model <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model, plotfun = "ppc_bars", nreps = 50)


set.seed(84735)
susceptibility_model2 <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total + Time1_impact_of_events_scale_total*Time1_five_factor_mindfulness_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model2, plotfun = "ppc_bars", nreps = 50)



set.seed(84735)
susceptibility_model3 <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total + Time1_impact_of_events_scale_total*Time1_five_factor_mindfulness_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total + Time1_patient_health_questionnaire_total*Time1_five_factor_mindfulness_questionnaire_total + Time1_impact_of_events_scale_total*Time1_patient_health_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model3, plotfun = "ppc_bars", nreps = 50)


set.seed(84735)
susceptibility_model4 <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_Age + Time1_patient_health_questionnaire_total +  Time1_five_factor_mindfulness_questionnaire_total + Time1_patient_health_questionnaire_total*Time1_five_factor_mindfulness_questionnaire_total + Time1_Age*Time1_patient_health_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model4, plotfun = "ppc_bars", nreps = 50)
#not a good one

set.seed(84735)
susceptibility_model5 <- stan_glm(Time1_perceived_susceptibility_to_COVID19 ~ Time1_patient_health_questionnaire_total +  Time1_five_factor_mindfulness_questionnaire_total + Time1_patient_health_questionnaire_total *Time1_five_factor_mindfulness_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model5, plotfun = "ppc_bars", nreps = 50)
```

### this one is slightly better... a couple preditions getting the peaks.. how can we get more to follow them?

### try time 2
```{r}
set.seed(84735)
susceptibility_model5 <- stan_glm(Time2_perceived_susceptibility_to_covid19 ~ Time2_patient_health_questionnaire_total +  Time2_impact_of_events_scale_total + Time2_intolerance_of_uncertainty_total + Time2_five_factor_mindfulness_questionnaire_total,  
                             data = covid,
                             family = poisson(),
                             chains = 4,
                             iter = 5000*2)

pp_check(susceptibility_model5, plotfun = "ppc_bars", nreps = 50)
```

## to disease
### try predicting percieved vulnerability to disease instead of COVID: approx normal distrib for this response var distrib

#Time 2 is better for prediction for disease vul
```{r echo=TRUE, results = 'hide'}
set.seed(84735)
disease_mod <- stan_glm(Time2_perceived_vulnerability_to_disease_total ~ Time2_Illnesses + Time2_patient_health_questionnaire_total + Time2_intolerance_of_uncertainty_total + Time2_Illnesses*Time2_patient_health_questionnaire_total,
                        data = covid,
                        family = gaussian(),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(disease_mod, nreps = 50)
```

```{r echo=TRUE, results = 'hide'}
set.seed(84735)
disease_mod2 <- stan_glm(Time2_perceived_vulnerability_to_disease_total ~ Time1_Age +  Time2_general_health_questionnaire_total +   *Time2_general_health_questionnaire_total,
                        data = covid,
                        family = gaussian(),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(disease_mod2, nreps = 50)




set.seed(84735)
disease_mod3 <- stan_glm(Time2_perceived_vulnerability_to_disease_total ~ Time2_Illnesses + Time2_Meds + Time2_intolerance_of_uncertainty_total + Time2_impact_of_events_scale_total + Time2_Illnesses*Time2_Meds + Time2_intolerance_of_uncertainty_total*Time2_impact_of_events_scale_total,
                        data = covid,
                        family = gaussian(),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(disease_mod3, nreps = 50)


set.seed(84735)
disease_mod4 <- stan_glm(Time2_perceived_vulnerability_to_disease_total ~ Time2_Illnesses + Time2_Meds + Time2_intolerance_of_uncertainty_total + Time2_quality_of_life_total + Time2_impact_of_events_scale_total + Time2_Illnesses*Time2_Meds + Time2_intolerance_of_uncertainty_total*Time2_impact_of_events_scale_total + Time2_quality_of_life_total*Time2_Illnesses,
                        data = covid,
                        family = gaussian(),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(disease_mod4, nreps = 50)
```

### Getting better.... can it be improved???
###The best of these is in the main RMD



# PREDICTING PPE USE

Time1_preventive_action_taken_scale_PPEuse
  predictors: age, illnesses, Time1_impact_of_events_scale_total, Time1_Religious_Affiliation, Time1_five_factor_mindfulness_questionnaire_total, Time1_number_of_times_leave_home_per_day, Time1_intolerance_of_uncertainty_total, Time1_patient_health_questionnaire_total, Time1_Educational_attainment
  
```{r echo=TRUE, results = 'hide'}
set.seed(84735)
cov_mod2 <- stan_glm(Time1_preventive_action_taken_scale_PPEuse ~
Time1_Age + Time1_perceived_susceptibility_to_COVID19 + Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total + Time1_Illnesses + Time1_intolerance_of_uncertainty_total + Time1_Illnesses*Time1_patient_health_questionnaire_total +
Time1_perceived_vulnerability_to_disease*Time1_patient_health_questionnaire_total + Time1_perceived_vulnerability_to_disease*Time1_Illnesses + Time1_intolerance_of_uncertainty_total*Time1_impact_of_events_scale_total,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(cov_mod2, nreps = 50)


set.seed(84735)
cov_mod4 <- stan_glm(Time1_preventive_action_taken_scale_PPEuse ~
Time1_Age + Time1_perceived_susceptibility_to_COVID19 + Time1_impact_of_events_scale_total + Time1_general_health_quetionnaire_total + Time1_Illnesses + Time1_intolerance_of_uncertainty_total + Time1_Illnesses*Time1_general_health_quetionnaire_total +
Time1_perceived_vulnerability_to_disease*Time1_general_health_quetionnaire_total + Time1_perceived_vulnerability_to_disease*Time1_Illnesses + Time1_intolerance_of_uncertainty_total*Time1_impact_of_events_scale_total,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(cov_mod4, nreps = 50)


#try travel avoid scale instead of ppe use
set.seed(84735)
cov_mod5 <- stan_glm(Time1_preventive_action_taken_scale_avoid_travel_people ~
Time1_Age + Time1_perceived_susceptibility_to_COVID19 + Time1_impact_of_events_scale_total + Time1_general_health_quetionnaire_total + Time1_Illnesses + Time1_intolerance_of_uncertainty_total + Time1_Illnesses*Time1_general_health_quetionnaire_total +
Time1_perceived_vulnerability_to_disease*Time1_general_health_quetionnaire_total + Time1_perceived_vulnerability_to_disease*Time1_Illnesses + Time1_intolerance_of_uncertainty_total*Time1_impact_of_events_scale_total,
                     data = covid,
                     family = poisson(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(cov_mod5, nreps = 50)

set.seed(84735)
cov_mod6 <- stan_glm(Time1_preventive_action_taken_scale_avoid_travel_people ~
Time1_Age + Time1_Gender + Time1_Marital_status +  Time1_five_factor_mindfulness_questionnaire_total + Time1_Religious_Affiliation + Time1_Age*Time1_Marital_status,
                     data = covid,
                     family = poisson(),
                     chains = 4,
                     iter = 5000*2)
                       
pp_check(cov_mod6, nreps = 50)

```
### *IF* we can capture the bimodality of PPE use / travel distribution: could be useful!

## predicting time 2 instead
```{r echo=TRUE, results = 'hide'}
set.seed(84735)
cov_mod3 <- stan_glm(Time2_preventive_action_taken_scale_PPEuse ~ Time1_Age + Time2_Illnesses + Time2_five_factor_mindfulness_questionnaire_total + Time2_patient_health_questionnaire_total +  Time2_patient_health_questionnaire_total*Time2_Illnesses,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(cov_mod3, nreps = 50)
```
### still does not capture the bimodality 



# PREDICTING IMPACT OF EVENTS
```{r echo=TRUE, results = 'hide'}
set.seed(84735)
impact <- stan_glm(Time1_impact_of_events_scale_total ~ Time1_Race + Time1_Age +  Time1_intolerance_of_uncertainty_total + Time1_patient_health_questionnaire_total + Time1_five_factor_mindfulness_questionnaire_total + Time1_preventive_action_taken_scale_PPEuse + Time1_Age*Time1_preventive_action_taken_scale_PPEuse + Time1_patient_health_questionnaire_total*Time1_preventive_action_taken_scale_PPEuse,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)
                       
                       
pp_check(impact, nreps = 50)
```
### Need to capture the bimodality 


```{r echo=TRUE, results = 'hide'}
set.seed(84735)
impact2 <- stan_glm(Time1_impact_of_events_scale_total ~ Time1_intolerance_of_uncertainty_total + Time1_patient_health_questionnaire_total + Time1_intolerance_of_uncertainty_total*Time1_patient_health_questionnaire_total,
                     data = covid,
                     family = gaussian(),
                     chains = 4,
                     iter = 5000*2)

pp_check(impact2, nreps = 50)
```

### Need to capture bimodality
### Possibly poisson instead of gaussian?


# PREDICTING SELF-ISOLATION (binary variable using logistic regression)
## Copied in the main RMD
```{r echo=TRUE, results = 'hide'}
covid_bin <- covid %>%
  mutate(Time1_self_isolation_yes_or_no = if_else(Time1_self_isolation_yes_or_no == '1', '0', '1')) %>%
    mutate(Time1_self_isolation_yes_or_no = as.integer(Time1_self_isolation_yes_or_no))

set.seed(84735)
log_mod <- stan_glm(Time1_self_isolation_yes_or_no   ~ Time1_patient_health_questionnaire_total +  Time1_impact_of_events_scale_total + Time1_patient_health_questionnaire_total*Time1_impact_of_events_scale_total ,
                        data = covid_bin,
                        family = binomial('logit'),
                        chains = 4,
                        iter = 5000 * 2)

pp_check(log_mod, nreps = 50)
```
