---
title: "natalia"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bayesrules)
library(rstan)
library(readr)
library(rstanarm)
```

```{r}
covid <- read_csv("time1Time2Data.csv")
```

```{r}
covid %>%
  select(Time1_Age,Time1_Race, Time1_Illnesses, Time1_impact_of_events_scale_total, Time1_Educational_attainment, Time1_meds, Time1_patient_health_questionnaire_total,Time1_perceived_susceptibility_to_COVID19 ,Time1_general_health_quetionnaire_total, Time1_Employment_After_COVID, Time1_intolerance_of_uncertainty_total, Time1_intolerance_of_uncertainty_total, Time1_Gender, Time1_perceived_vulnerability_to_disease,Time1_self_isolation_yes_or_no,Time1_number_of_times_leave_home_per_day, Time1_preventive_action_taken_scale_avoid_travel_people,Time1_Marital_status, Time1_five_factor_mindfulness_questionnaire_total, Time1_Religious_Affiliation, Time1_preventive_action_taken_scale_avoid_travel_people, Time1_preventive_action_taken_scale_PPEuse, Time1_quality_of_life_Total) %>%
  as.data.frame() %>%
  cor(use="complete.obs")
```

```{r}
covid %>%
  select(Time2_Annual_income,Time2_Illnesses,Time2_Meds, Time2_impact_of_events_scale_total, Time2_employment_status, Time2_patient_health_questionnaire_total, Time2_intolerance_of_uncertainty_total ,Time2_perceived_susceptibility_to_covid19 ,Time2_self_isolation_yes_or_no, Time2_five_factor_mindfulness_questionnaire_total, Time2_general_health_questionnaire_total, Time2_perceived_vulnerability_to_disease_total,Time2_preventive_action_taken_scale_PPEuse, Time2_quality_of_life_total) %>%
  as.data.frame() %>%
  cor(use="complete.obs")
```


reponse variables of interest: 

Time1_perceived_susceptibility_to_COVID19 
  predictors: Time1_patient_health_questionnaire_total, Time1_impact_of_events_scale_total, Time1_intolerance_of_uncertainty_total, Time1_perceived_vulnerability_to_disease, Time1_five_factor_mindfulness_questionnaire_total   
  
```{r}
#Miles said to try Poisson
set.seed(84735)
susceptibility_model <- stan_glm(Time2_perceived_susceptibility_to_covid19 ~ Time2_patient_health_questionnaire_total + Time2_perceived_vulnerability_to_disease_total + Time2_patient_health_questionnaire_total*Time2_perceived_vulnerability_to_disease_total,  
                             data = covid,
                             family = poisson,
                             chains = 4,
                             iter = 10000*2)


set.seed(84735)
pp_check(susceptibility_model, nreps = 50)
#still not relaly working, not a good variable to try to predict maybe
```
  
  
  
Time1_self_isolation_yes_or_no  
  predicotrs: Time1_impact_of_events_scale_total, Time1_patient_health_questionnaire_total, ime1_general_health_quetionnaire_total, Time1_preventive_action_taken_scale_PPEuse    


Time1_number_of_times_leave_home_per_day
  predictors: age, race, illnesses, Time1_impact_of_events_scale_total, Time1_patient_health_questionnaire_total, Time1_perceived_susceptibility_to_COVID19, Time1_preventive_action_taken_scale_PPEuse          


Time1_preventive_action_taken_scale_PPEuse
  predictors: age, illnesses, Time1_impact_of_events_scale_total, Time1_Religious_Affiliation, Time1_five_factor_mindfulness_questionnaire_total, Time1_number_of_times_leave_home_per_day, Time1_intolerance_of_uncertainty_total, Time1_patient_health_questionnaire_total, Time1_Educational_attainment 

```{r}

```


Time1_quality_of_life_Total
  predictors: illnesses, health_questionairere, percieved suscept, mindfulness, general health quest, percieved vuln to dieasease 
  
```{r} 
set.seed(84735)
quality_mod1 <- stan_glm(Time1_quality_of_life_Total ~ Time1_patient_health_questionnaire_total + Time1_perceived_vulnerability_to_disease + Time1_five_factor_mindfulness_questionnaire_total + Time1_patient_health_questionnaire_total*Time1_perceived_vulnerability_to_disease, 
                             data = covid,
                             family = gaussian(),
                             chains = 4,
                             iter = 10000*2)

set.seed(84735)
pp_check(quality_mod1, nreps = 50)
```


from the paper:
The Impact of Events Scale – Revised (IES-R) was used to measure post-traumatic stress symptoms (Weiss & Marmar, 1997). The IES-R has been extensively used as a measure of post-traumatic stress symptoms in community and clinical samples (e.g., Beck, et al., 2008). The scale contains 22 items (e.g. “I thought about it when I didn’t mean to”) that were responded to on a five-point scale that ranged from 0 (“not at all”) to 4 (“extremely”). Participants were instructed to indicate how distressing each difficulty has been for the past 7 days with respect to the Coronavirus situation. The internal consistency of the scale was high (Cronbach’s α = .97). A total IES-R score was calculated with higher scores indicating higher levels of symptoms.


could have impact of events total as outcome